Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-08-06 paper/paper.Rmd
some more revisions to spatial blocking section

The "Spatial blocking" from package \pkg{blockCV} comes with various blocking options such as random (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`).
Additionally, the user might supply a numeric value in meters via argument `range` which will ensure a quadratic block pattern across the study area.
This kind of blocking might be of special interest for species distribution modeling as well as the possibility to supply a user-defined polygon via argument `rasterLayer` with predefined blocking zones.

This procedure supports both random and systematic resampling of square blocks (argument `selection = "random"` and `"systematic"`, respectively).
Block sizes in meters) are determined by the `range` argument.
Alternatively, rectangular blocks can be created by specifying the number of desired rows and columns (arguments `rows` and `cols`).

>>>>

Block-level resampling from package \pkg{blockCV} supports both random and systematic resampling of square blocks (`method = "spcv_block"` with argument `selection = "random"` and `"systematic"`, respectively; Figure&nbpsp;~\@ref(fig:block-random) and \@ref(fig:block-systematic)).
The implementation in \pkg{blockCV} has specific options that are designed for modeling presence-only data, which is a typical situation in species distribution modeling.
Users can also supply a user-defined polygon via argument `rasterLayer` with predefined blocking zones.

Block sizes (in meters) are determined by the `range` argument.
Alternatively, rectangular blocks can be created by specifying the number of desired rows and columns (arguments `rows` and `cols`).
